\bf Optimization of String Rewriting Operations for 3D Fractal Generation with Genetic Algorithms

### 2018-10-25 Optimization-of-String-Rewriting-Operations-for-3D-Fractal-Generation-with-Genetic-Algorithms/abstract.tex
Small modifications were done.

\author{Todor Balabanov, Kolyu Kolev, Janeta Sevova \\
Institute of Information and Communication Technologies \\
Bulgarian Academy of Sciences \\
acad. Georgi Bonchev Str, block 2, office 514, 1113 Sofia, Bulgaria \\
todorb@iinf.bas.bg \\
http://www.iict.bas.bg/}

>>>>

\author{Todor Balabanov, Janeta Sevova, Kolyu Kolev \\
Institute of Information and Communication Technologies \\
Bulgarian Academy of Sciences \\
acad. Georgi Bonchev Str, block 2, office 514, 1113 Sofia, Bulgaria \\
kkolev@iit.bas.bg \\
http://www.iict.bas.bg/}
